\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}

\def\Name{Ran Liao}
\def\Topic{Maintenance}

\title{\textbf{\Topic}}
\author{\Name}
\markboth{Notes on \Topic\ }{Notes on \Topic\ }
\date{\today}
 
\pagestyle{fancy}
\fancyhf{}
\rhead{\date{\today} }
\lhead{Notes on \Topic\ }
\rfoot{\thepage}

\textheight=9in
%\textwidth=6.5in
\topmargin=-.75in
%\oddsidemargin=0in
%\evensidemargin=0in
 
\begin{document}
\maketitle
\noindent\makebox[\linewidth]{\rule[8pt]{5in}{0.5pt}}

\section*{Terminology}

\begin{enumerate}

	\item \textbf{Maintenance}
	
	Maintenance is the process that occurs when a software artifact is modified because of a problem or because of a need for improvement or adaptation.
	It occurs whenever software is modified regardless of whether this takes place before or after installation of the software product.
	
	\item \textbf{Postdelivery Maintenance}
	
	Any change to any component of the product (including documentation) after it has passed the acceptance test.

\end{enumerate}

 
\section*{Catagory}
 
\begin{enumerate}

	\item \textbf{Corrective maintenance}
	
	To correct residual faults. 
	
	e.g. analysis, design, implementation, documentation, or any other type of faults.
	
	\item \textbf{Perfective maintenance}
	
	Client requests changes to improve product effectiveness.

	e.g. add additional functionality, make product run faster, improve maintainability.
	
	\item \textbf{Adaptive maintenance}
	
	Responses to changes in the environment in which the product operates.
	
	e.g. the product is ported to a new compiler, operating system, and/or hardware.

\end{enumerate}

\section*{Obstacles for Maintenance of Object-Oriented Software}

Inheritance and polymorphism can have a positive effect on development, but a negative effect on maintenance.

\begin{enumerate}

	\item \textbf{The complete inheritance hierarchy can be large}
	
	The inheritance tree may be spread over the entire product.
	
	\item \textbf{The consequences of polymorphism and dynamic binding}
	
	It takes extra efforts to determine which version of a polymorphic function is actual the buggy one.
		
	\item \textbf{The consequences of inheritance}
	
	Modify a superclass will affect all descendent subclasses.
	
	i.e. ``Fragile base class problem"
	
\end{enumerate}
\end{document}